A Gaussian process model of human e\-lect\-ro\-cort\-i\-co\-graph\-ic data

### 2020-04-18 paper/rev1.tex

\documentclass[11pt]{article}
\usepackage[round,sort&compress]{natbib}
\setcitestyle{aysep={}}
\usepackage{newpxtext,newpxmath}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left]{lineno}
%\linenumbers

@@

\section*{Discussion} Are our brain's networks static or dynamic?  And to what
extent are the network properties of our brains stable across people and tasks?
One body of work suggests that our brain's \textit{functional} networks are
dynamic~\citep[e.g., ][]{MannEtal18, OwenEtal19}, person-specific~\citep[e.g.,
][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.  In contrast,
although the gross anatomical structure of our brains changes meaningfully over
the course of years as our brains develop, on the timescales of typical
neuroimaging experiments (i.e., hours to days) our anatomical networks are
largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many aspects of brain
anatomy, including white matter structure, are largely preserved across
people~\citep[e.g., ][]{TalaTour88, JahaEtal13, MoriEtal08}. There are several
possible means of reconciling this apparent inconsistency between dynamic
person- and task-specific functional networks versus stable anatomical networks.
For example, relatively small magnitude anatomical differences across people may
be reflected in reliable functional connectivity differences.  Along these
lines, one recent study found that diffusion tensor imaging (DTI) structural
data is similar across people, but may be used to predict person-specific
resting state functional connectivity data~\citep{BeckEtal18}.  Similarly, other
work indicates that task-specific functional activations may be predicted by
resting state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.
Another (potentially complementary) possibility is that our functional networks
are constrained by anatomy, but nevertheless exhibit (potentially rapid)
task-dependent changes~\citep[e.g., ][]{SporBetz16}.  This prior work differs
from ours in a number of ways.  For example, fMRI data has substantially higher
spatial resolution than (raw) ECoG data, and fMRI data have nearly complete
spatial overlap across participants whereas ECoG data have minimal spatial
overlap across participants.  Nevertheless, our work draws inspiration from
those studies in that we also attempt to estimate held-out activity patterns
across people and tasks.

@@

Another important finding is that SuperEEG-based reconstructions accurately
recover activity patterns at a broad range of frequencies (as well as broadband
patterns).  However, brain networks differed in how informative they were about
activity within each frequency band.  Prior work has largely treated
region-specific narrowband and broadband activity as an indicator that activity
at those frequency ranges reflects that the given region is representing or
supporting a particular function.  Our work suggests a complementary
interpretation that when we observe a particular neural pattern in a particular
brain region, it may instead (or in addition) reflect how that region is
transmitting information to the rest of the brain via signalling at the given
frequency range.

>>>>

\documentclass[11pt]{article}
\usepackage[round,sort&compress]{natbib}
\setcitestyle{aysep={}}
\usepackage{newpxtext,newpxmath}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left]{lineno}
\linenumbers

@@

Taken together, the frequency-specific information maps suggest a potential new
interpretation of many of the above previously reported findings.  Prior work
has largely treated region-specific narrowband and broadband activity as an
indicator that activity at those frequency ranges reflects that the given region
is representing or supporting a particular function.  Our work suggests an
alternative interpretation that when we observe a particular neural pattern in a
particular brain region, it may instead reflect how that region is 
transmitting information to the rest of the brain via signalling at the given
frequency range.

\section*{Discussion}
Are our brain's networks static or dynamic?  And to what
extent are the network properties of our brains stable across people and tasks?
One body of work suggests that our brain's \textit{functional} networks are
dynamic~\citep[e.g., ][]{MannEtal18, OwenEtal19}, person-specific~\citep[e.g.,
][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.  In contrast,
although the gross anatomical structure of our brains changes meaningfully over
the course of years as our brains develop, on the timescales of typical
neuroimaging experiments (i.e., hours to days) our anatomical networks are
largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many aspects of brain
anatomy, including white matter structure, are largely preserved across
people~\citep[e.g., ][]{TalaTour88, JahaEtal13, MoriEtal08}. There are several
possible means of reconciling this apparent inconsistency between dynamic
person- and task-specific functional networks versus stable anatomical networks.
For example, relatively small magnitude anatomical differences across people may
be reflected in reliable functional connectivity differences.  Along these
lines, one recent study found that diffusion tensor imaging (DTI) structural
data is similar across people, but may be used to predict person-specific
resting state functional connectivity data~\citep{BeckEtal18}.  Similarly, other
work indicates that task-specific functional connectivity may be predicted by
resting state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.
Another (potentially complementary) possibility is that our functional networks
are constrained by anatomy, but nevertheless exhibit (potentially rapid)
task-dependent changes~\citep[e.g., ][]{SporBetz16}.

@@
